Direction-Free In-Air Signature Verification Using WIFI CSI Signal

### 2019-05-09 190410_Paper_ACPR/paper_v0.tex
Paper_ACPR: related1

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Koch, Gregory, Richard Zemel, and Ruslan Salakhutdinov.
 "Siamese neural networks for one-shot image recognition." 
 ICML deep learning workshop. Vol. 2. 2015.

>>>>

% Meaning of CSI
%[From Halperin paper]
CSI captures signal strength and phase information for OFDM subcarriers and between each pair of transmit-receive antennas.
It runs on a commodity 802.11n NIC, and records Channel State Information (CSI) based on the 802.11 standard.
The CSI contains information about the channel between sender and receiver at the level of individual data subcarriers, for each pair of transmit and receive antennas.
%[From Halperin End]

% Structure of CSI
%[From HC's ELM paper]
In a frequency domain, the CSI of sub-carrier $\mathbf{c}$ between transmitter(Tx) and receiver(Rx) can be modeled as 
$\mathnormal{R}_{c} = \mathbf{H}_{c}\mathnormal{T}_{c} +\mathnormal{N}$ where the $\mathnormal{R}_{c}$ and $\mathnormal{T}_{c}$  denote the received and the transmitted signal vector of dimension $\mathnormal{r}$ and $\mathnormal{t}$, respectively. The $\mathnormal{N}$ is the additive channel noise and $\mathbf{H}_{c}$ is the $\mathnormal{r}\times\mathnormal{t}$ channel matrix. The CSI of sub-carrier $\mathnormal{c}$ can be modeled as follows:
\begin{equation}
    \mathnormal{h}_{c} = \mid\mathnormal{h}_{c}\mid\mathnormal{e}^{\angle\theta},
\end{equation}
where $\mid\mathnormal{h}_{c}\mid$ and $\theta$ represent the amplitude and the phase of the sub-carrier, respectively.
%[From HC's ELM end]

\subsection{Siamese Networks}
- An In-Air Signature Verification System Using Wi-Fi Signals

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
% Deep Learning Siamese Paper
\bibitem{ref_article1}
Koch, Gregory, Richard Zemel, and Ruslan Salakhutdinov.
 "Siamese neural networks for one-shot image recognition." 
 ICML deep learning workshop. Vol. 2. 2015.
% HC's Conference Paper
 \bibitem{ref_article2}
Moon, Han-Cheol, et al. "An In-Air Signature Verification System Using Wi-Fi Signals." Proceedings of the 2017 4th International Conference on Biomedical and Bioinformatics Engineering. ACM, 2017.
% JS's Conf Paper
\bibitem{ref_article3}
JS's Conf Paper
% Halperin CSI tool paper
\bibitem{ref_article4}
Halperin, Daniel, et al. "Tool release: Gathering 802.11 n traces with channel state information." ACM SIGCOMM Computer Communication Review 41.1 (2011): 53-53.
